---
title: "Initial Study - Negative Projection"
author: "Kathryn Denning"
date: "Originally analyzed Fall 2017 - Updated for publication December 2019"
output: 
    html_document:
      code_download: TRUE
      toc: TRUE
      toc_float:
        collapsed: FALSE
      toc_depth: 1
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
#loading packages
library(foreign)
library(reshape2)
library(tidyverse)
library(dplyr)
library(car)
library(haven)
library(psych)
library(lmerTest)
library(sjPlot)
library(reshape2)
library(data.table)
library(emmeans)
library(effects)
library(Cairo)
library(tinytex)

#making it round to three decimal places
options(scipen = 999)
knitr::opts_knit$set(dev.args = list(type = "cairo"))

#Setting global chunk options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

#importing data with IP address and lat/long to look for MTurk bots
bot_check <- Import("ppt1_with lat long to check bots.csv") 

bot_check <- bot_check[-c(1,2),,drop = F] 

#importing the data that has been reviewed for completion of PT task
wide_data <- Import("ppt1_fulldata_ptcleanedonly.xlsx") 

#dropping the longer description of each question
wide_dropped1 <- wide_data[-c(1),,drop = F] 
```

```{r, include = FALSE}
#removing repeat IP addresses since those often indicate bots
#getting a dataset with only subid and IPAdress
ip <- bot_check %>% 
  select(subid, IPAddress)

#identifying the repeat IP addresses
repeat_ips <- ip$IPAddress[duplicated(ip$IPAddress)]

#getting the corresponding subids
bot_check %>% 
  select(subid, IPAddress, LocationLatitude, LocationLongitude) %>% 
  filter(IPAddress %in% c("24.241.223.182", "72.79.119.56", "108.230.124.237", "172.97.7.163", "67.236.228.7", "68.190.36.43"))

#removing the subids from the overall dataset that has already been cleaned to remove people who did not correctly complete the PT narrative task
no_bots <- wide_data %>% 
  filter(!subid %in% c(96, 99, 166, 167, 171, 239, 265, 345, 613, 758, 778, 779))

# Drop row of question labels
no_bots <- no_bots[-c(1),]
```

```{r data cleaning, include = FALSE}
#Data cleaning
clean_data <- no_bots %>% 
  ## drop two MFQ items that aren't actually the survey - 6, 22 in each
select(-MFQSelf_6, -MFQSelf_22, -MFQTrump_6, -MFQTrump_22, -MFQClin_6,
       -MFQClin_22, -MFQTarg_6, -MFQTarg_22) %>% 
  ## dropping PANAS and exploratory items for this study to make data more manageable
  select(-c(PANAS1_1:PANAS1_20, PANAS2_1:PANAS2_20, WilltoDiscuss:Liking, 
            gender_writein, race_writein, birth_writein, race_writein, 
            language_writein, raise_writein)) %>% 
  ### Wrangling data to get MFQ for self, MFQ to targ, MFQ for stereotype, column for candidate, average of IG identification
  pivot_longer(c(MFQSelf_1:MFQSelf_32,
                 MFQTrump_1:MFQTrump_32,
                 MFQClin_1:MFQClin_32,
                 MFQTarg_1:MFQTarg_32),
               names_sep = "_",
               names_to = c("mfq_type", "MFQ_Number")) %>% 
  pivot_wider(names_from = mfq_type, values_from = value) %>% 
  pivot_longer(IG_Clin_1:IG_Trump_14,
               names_sep = "_",
               names_to = c("ident", "ident_targ", "ident_num")) %>% 
  pivot_wider(names_from = ident, values_from = value) %>% 
  rename(ident = IG) %>% 
  filter(!is.na(ident)) %>% 
  #making candidate they voted for a factor
  mutate(Cand_votedfor = ifelse(ident_targ == "Clin", 1, 
                                ifelse(ident_targ == "Trump", 0, NA))) %>% 
  pivot_longer(Day_Clin_In_PT:Day_Trump_In_C,
               names_to = c("Day_key")) %>% 
  rename(Day_content = value) %>% 
  mutate(Day_key = as.factor(Day_key)) %>% 
  filter(!is.na(Day_content)) %>% 
  mutate(inoutgroup = fct_collapse(Day_key, 
                                   Ingroup = c("Day_Clin_In_C", 
                                                "Day_Clin_In_PT", 
                                                "Day_Trump_In_C", 
                                                "Day_Trump_In_PT"), 
                                   Outgroup = c("Day_Clin_Out_C", 
                                                "Day_Clin_Out_PT",
                                                "Day_Trump_Out_C", 
                                                "Day_Trump_Out_PT")),
         PT = fct_collapse(Day_key,
                           PT = c("Day_Clin_In_PT",
                                  "Day_Trump_In_PT",
                                  "Day_Clin_Out_PT",
                                  "Day_Trump_Out_PT"),
                           control = c("Day_Clin_In_C",
                                       "Day_Trump_In_C",
                                       "Day_Clin_Out_C",
                                       "Day_Trump_Out_C")),
         par_cand = fct_collapse(Day_key,
                                  Clinton = c("Day_Clin_In_PT",
                                           "Day_Clin_Out_PT",
                                           "Day_Clin_In_C",
                                           "Day_Clin_Out_C"),
                                  Trump = c("Day_Trump_In_PT",
                                            "Day_Trump_Out_PT",
                                            "Day_Trump_In_C",
                                            "Day_Trump_Out_C")),
         targ_cand = fct_collapse(Day_key,
                                  Clinton = c("Day_Clin_In_PT",
                                              "Day_Clin_In_C",
                                              "Day_Trump_Out_PT",
                                              "Day_Trump_Out_C"),
                                  Trump = c("Day_Clin_Out_PT",
                                            "Day_Clin_Out_C",
                                            "Day_Trump_In_PT",
                                            "Day_Trump_In_C")))

clean_data[,1:26] <- sapply(clean_data[,1:26],as.numeric)
clean_data[,28:30] <- sapply(clean_data[,28:30],as.numeric)

  #average of ingroup-identification for each subjut
clean_data2 <- clean_data %>% 
  #effects coding for group with ingroup = .5 and outgorup = -.5, for PT .5 = PT and Control = -.5
  mutate(inoutgroup_effects = ifelse(inoutgroup == "Ingroup", .5,
                                     ifelse(inoutgroup == "Outgroup", -.5, NA)),
         PT_effects = ifelse(PT == "PT", .5, 
                             ifelse(PT == "control", -.5, NA)),
         targ_cand = ifelse(targ_cand == "Clinton", 1, 
                            ifelse(targ_cand == "Trump", 2, NA))) %>% 
  #grand mean centering MFQ for self
  mutate(MFQSelf_c = MFQSelf - mean(MFQSelf, na.rm = TRUE)) %>%  
  #removing people who failed the manipulation check
  filter(targ_cand == 1 & Man_TargVote == 1 | 
           targ_cand == 2 & Man_TargVote == 2) %>%
  select(-Day_content, -Day_key) %>% 
  #effects coding candidate
  mutate(Targ_Cand_effectscoded = ifelse(targ_cand == "1", .5, 
                                         ifelse(targ_cand == "2", -.5, NA))) %>% 
  group_by(subid) %>% 
  mutate(ident_subave = mean(ident)) %>% 
  filter(!is.na(ident_subave))

#for some reason, this wouldn't work in the piping above, so had to hard code it
#grand mean centering for ingroup identification
clean_data2$ident_c <- clean_data2$ident_subave - mean(clean_data2$ident_subave, na.rm = TRUE)
clean_data2$Gender <- as.factor(clean_data2$Gender)
levels(clean_data2$Gender) <- c("Male", "Female", "Other")
clean_data2$Race <- as.factor(clean_data2$Race)
levels(clean_data2$Race) <- c("American Indian/Native Alaskan", 
                             "Asian", 
                             "Black",
                             "Latinx",
                             "Middle Eastern",
                             "Caucasian",
                             "Multiracial",
                             "Other")
#data with just the variables for the analysis
model_data <- clean_data2 %>% 
  select(subid, MFQ_Number, MFQSelf_c, MFQTarg, ident_c, PT_effects, 
         inoutgroup_effects) %>%
  unique() %>% 
  na.omit()
```

# Demographics & Descriptives {.tabset .tabset-fade .tabset-pills}

## N in in/outgroup conditions

```{r descrip n in conditions}
clean_data2 %>% 
  select(subid, inoutgroup) %>% 
  na.omit() %>% 
  unique() %>% 
  group_by(inoutgroup) %>% 
  count()
```

## N with demographic information

```{r n reported dem info}
dem <- clean_data2 %>% 
  select(subid, MFQ_Number, MFQSelf_c, MFQTarg, ident_c, PT_effects, 
         inoutgroup_effects, Gender, Race, Age, Edu_Part) %>%  
  unique %>% 
  na.omit() 

dem %>% 
  select(subid) %>% 
  unique() %>% 
  nrow()
```

## Gender

```{r gender}
dem %>% 
  select(subid, Gender) %>% 
  unique() %>% 
  na.omit() %>% 
  group_by(Gender) %>% 
  count()
```

## Race

```{r race}
dem %>% 
  select(subid, Race) %>% 
  unique() %>% 
  group_by((Race)) %>% 
  count() %>% 
  mutate(percent = n/668*100)
```

## Age

```{r age}
dem %>% 
  summarize(mean(Age)) %>% 
  summarize(mean = mean(`mean(Age)`),
            sd = sd(`mean(Age)`))
```

## Education

```{r education}
dem %>% 
  select(subid, Edu_Part) %>% 
  unique() %>% 
  group_by((Edu_Part)) %>% 
  count()

somecollege <- ((147+90+208+32+93+31)/668)*100
somecollege
```

## Alpha MFQ Self

### Overall

```{r MFQ self overall}
alpha_self <- clean_data2 %>% 
  select(subid, MFQ_Number, MFQSelf) %>% 
  unique() %>% 
  na.omit() %>% 
  pivot_wider(names_from = MFQ_Number, values_from = MFQSelf)

alpha_self <- alpha_self[-1] 

psych::alpha(alpha_self)
```

### Harm

```{r harm alpha self}
harm_self <- alpha_self %>% 
  select(c("1", "7", "12", "17", "23", "28"))
psych::alpha(harm_self)
```

### Fairness

```{r fairness alpha self}
fair_self <- alpha_self %>% 
  select(c("2", "8", "13", "18", "24", "29"))
psych::alpha(fair_self)
```

### Ingroup

```{r ingroup alpha self}
ingroup_self <- alpha_self %>% 
  select(c("3", "9", "14", "25", "30"))
psych::alpha(ingroup_self)
```

### Authority

```{r authority alpha self}
authority_self <- alpha_self %>% 
  select(c("4", "10", "15", "26", "31"))
psych::alpha(authority_self)
```

### Purity

```{r purity alpha self}
purity_self <- alpha_self %>% 
  select(c("5", "11", "16", "27", "32"))
psych::alpha(purity_self)
```

## Alpha MFQ Target

### Overall

```{r MFQ alpha targ overall}
alpha_targ <- clean_data2 %>% 
  select(subid, MFQ_Number, MFQTarg) %>% 
  unique() %>% 
  na.omit() %>% 
  pivot_wider(names_from = MFQ_Number, values_from = MFQTarg)

alpha_targ <- alpha_targ[-1] 

psych::alpha(alpha_targ)
```

### Harm

```{r harm alpha targ}
harm_targ <- alpha_targ %>% 
  select(c("1", "7", "12", "17", "23", "28"))
psych::alpha(harm_targ)
```

### Fairness

```{r fairness alpha targ}
fair_targ <- alpha_targ %>% 
  select(c("2", "8", "13", "18", "24", "29"))
psych::alpha(fair_targ)
```

### Ingroup

```{r ingroup alpha targ}
ingroup_targ <- alpha_targ %>% 
  select(c("3", "9", "14", "25", "30"))
psych::alpha(ingroup_targ)
```

### Authority

```{r authority alpha targ}
authority_targ <- alpha_targ %>% 
  select(c("4", "10", "15", "26", "31"))
psych::alpha(authority_targ)
```

### Purity

```{r purity alpha targ}
purity_targ <- alpha_targ %>% 
  select(c("5", "11", "16", "27", "32"))
psych::alpha(purity_targ)
```

## Alpha for in-group identification

```{r alpha for identification}
ir_ident <- clean_data2 %>% 
  select(subid, ident_num, ident) %>% 
  na.omit() %>% 
  unique() %>% 
  spread(ident_num, ident)

ir_ident <- subset(ir_ident, select = -c(subid))

alpha(ir_ident)
```

# Model {.tabset .tabset-fade .tabset-pills}

## Results

```{r model results}
#model
Model_Pro_random_effects <- lmer(MFQTarg ~ MFQSelf_c * inoutgroup_effects * 
                                   PT_effects * ident_c + (MFQSelf_c|subid), 
                                 data = model_data)

#results
tab_model(Model_Pro_random_effects,
          title = "Projection")

confint(Model_Pro_random_effects)
```

## Interaction plot: identification and group

```{r three-way plot set-up, include = FALSE}
# getting the information for the plot from the model in the correct format
describe(model_data$ident_c)
describe(model_data$inoutgroup_effects)

effects_threeway <- effect(term = "MFQSelf_c:inoutgroup_effects:ident_c", 
                           xlevels = list(ident_c = c(-1.8, 0, 1.8), 
                                         inoutgroup_effects = c(-.5,.5)), 
                           mod = Model_Pro_random_effects)

effects_threeway <- as.data.frame(effects_threeway)

effects_threeway$Group <- as.factor(effects_threeway$inoutgroup_effects)
effects_threeway$Identification <- as.factor(effects_threeway$ident_c)

ident_label <- c("-1.8" = "Low identification \n (1 SD below)", 
                 "0" = "Average identification",
                 "1.8" = "High identificatiion \n(1 SD above)")
```

```{r three-way plot color}
ggplot(effects_threeway, aes(MFQSelf_c, 
                             fit, 
                             group = Group, 
                             color = Group)) +
  geom_smooth(method = "lm") +
  facet_wrap(~Identification, labeller = 
               labeller(Identification = ident_label)) +
  scale_color_discrete("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group")) +
  theme_minimal() +
  labs(title = "Projection predicted by identification and target group",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
```

```{r three-way plot BW}
#Function to print plots to pngs for paper
# ggpreview <- function(...) {
#   fname <- tempfile(fileext = ".png")
#   ggsave(filename = fname, ...)
#   system2("open", fname)
#   invisible(NULL)
# }

knitr::opts_chunk$set(fig.width = 8, fig.height = 6) 

ggplot(effects_threeway, aes(MFQSelf_c, 
                             fit, 
                             group = Group, 
                             color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black", 
              aes(linetype = Group)) +
  facet_wrap(~Identification, labeller = 
               labeller(Identification = ident_label)) +
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                   "dashed")) +
  theme_minimal() +
  labs(title = "Projection predicted by identification and target group",
       x = "MFQ responses for self",
       y = "MFQ responses for target")


#ggpreview(width = 8, height = 6, units = "in")
```

## Plot: Main effect group

```{r main effect group plot set-up, include = FALSE}
# getting the information for the main effect of group
effects_main_group <- effect(term = "MFQSelf_c:inoutgroup_effects", 
                             xlevels = list(inoutgroup_effects = c(-.5,.5)), 
                             mod = Model_Pro_random_effects)

effects_main_group <- as.data.frame(effects_main_group)

effects_main_group$Group <- as.factor(effects_main_group$inoutgroup_effects)
```

```{r main effect group plot color}
ggplot(effects_main_group, aes(MFQSelf_c, 
                               fit, 
                               group = Group, 
                               color = Group)) +
  geom_smooth(method = "lm") +
  scale_color_discrete("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group")) +
  theme_minimal() +
  labs(title = "Projection predicted by target group",
       x = "MFQ responses for self",
       y = "MFQ responses for target")
```

```{r main effect group plot BW}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6) 

ggplot(effects_main_group, aes(MFQSelf_c, 
                               fit, 
                               group = Group, 
                               color = Group)) +
  geom_smooth(method = "lm", se = FALSE, size = .7, colour = "black",
              aes(linetype = Group)) +
  scale_linetype_manual("Group", breaks = c(-.5, .5), 
                       labels = c("Out-group", "In-group"),
                       values = c("solid", 
                                  "dashed")) +
  theme_minimal() +
  labs(title = "Projection predicted by target group",
       x = "MFQ responses for self",
       y = "MFQ responses for target")

# ggpreview(width = 8, height = 6, units = "in")
```

### Checking if in-group is significantly different from 0

```{r in diff from zero, echo=FALSE}
#model
model_ingroup <- lmer(MFQTarg ~ MFQSelf_c * inoutgroup_effects * PT_effects * 
                        ident_c + (MFQSelf_c|subid), data = model_data, 
                      subset = (model_data$inoutgroup_effects == 0.5))

#results
tab_model(model_ingroup,
          title = "Projection")

#rank deficient so can't include it because doesn't include all the comparisons
```

### Checking if out-group is significantly different from 0

```{r out diff from zero, echo=FALSE}
#model
model_outgroup <- lmer(MFQTarg ~ MFQSelf_c * inoutgroup_effects * PT_effects * 
                         ident_c + (MFQSelf_c|subid), 
                       data = model_data,
                       subset = (model_data$inoutgroup_effects == -0.5))

#results
tab_model(model_outgroup,
          title = "Projection")

#rank deficient so can't include it because doesn't include all the comparisons
```

# Perspective taking manipulation check

```{r pt manipulation check, echo=FALSE}
mancheck <- clean_data2 %>% 
  select(subid, Man_PT, PT_effects)

#PT manipulation check
mancheck_pt <- lm(Man_PT ~ PT_effects, data = mancheck)
summary(mancheck_pt)
confint(mancheck_pt)

# -.5 is control, .5 is PT
mancheck_pt_descrip <-summary(lsmeans(mancheck_pt,~PT_effects, 
                                      at = list(PT_effects = c(-.5,.5))))
mancheck_pt_descrip

ggplot(mancheck_pt_descrip , aes(x = PT_effects, y = lsmean))+
  geom_col()
```
